\section{Theoretical part}

\subsection{Domain Name System}
\subsubsection{DNS provisions}
The DNS system ensures fault tolerance on a packet level through UDP, which wraps the segments
in a header containing a checksum. On a system level fault tolerance is ensured because the system
is designed as a distributed architecture, making sure that there are no central points of failure.
Both of these techniques also ensure scalability by making making DNS have stateless connections and
spreading requests out over a large amount of servers. Efficiency is then also ensured because UDP has
a very low overhead compared to TCP, and one may query servers that are close.

\subsubsection{DNS lookup and format}
\begin{description}
    % 2-4 sentences
    \item[Part 1:] The CNAME record allows a server to be known through several aliases, such as
        a web-server being named www.domain.tld and a ftp service on the same server being named
        ftp.domain.tld. It may also be used to load-balance requests by returning CNAME records
        for a domain that redirect users to servers that are closer to them.
        %TODO: Can you set all CNAMES in the DNS or do you need something custom?
    % 4-8 sentences
    \item[Part 2:] Iterative lookups work by the root and TLD servers delegating further lookups
        to the requesting party, instead of performing them themselves. This means that the local
        DNS server that a client is asking will ask another server and receive an answer, then acting
        on the information in that answer to fulfill the request (by further lookups). In a recursive
        lookup the server that is being asked is the one that queries further servers for more detailed
        information, and it will only return once it has an authoritative answer.

        Iterative lookups place less strain on the DNS network, because only the local DNS server has
        to maintain state about the request that is being answered. This enables the system to scale
        better. The caches of the local DNS server will also be filled with information on authorative
        and TLD servers, cutting off the root level and speeding up requests.
        %TODO: When and why do we want recursive lookups?
        % Is it something about using it to fill caches?
    % Diagram
    \item[Part 3:]  
\end{description}

\subsection{Transport protocols}
\subsubsection{TCP reliability and utilization}
\begin{description}
    \item[Part 1:] The 3-way handshake ensures that both sides have received the starting segment number of the other side.
        If the final ACK is not sendt, the server cannot be certain that it's starting segment number has actually
        reached the client. If we wish to be sure that the connection is correctly initialized on both sides we must
        therefore use a 3-way-handshake.
    \item[Part 2:] TCP facilitates a full-duplex connection by making the ACK a field in the header of segments, thus
        allowing mixing an answer to a segment with a new data segment to be delivered to the other side. The setup also
        initializes the link in both directions, so both sides are ready to send to each other.
\end{description}

\subsubsection{Reliability vs overhead}
\begin{description}
    \item[Part 1:] TCP adds overhead both in the header (being approx. 20 bytes in size, compared to 8 bytes for UDP), and
        by requiring that all segments are acknowledged and optionally re-sent. It must also negotiate segment numbers before
        starting to transmit data, while UDP starts blasting data immediately.
    \item[Part 2:] 
\end{description}

\subsubsection{Use of transport protocols}
\begin{description}
    \item[DNS part 1:] DNS employs the UDP transport protocol. This is because it has a low overhead, does not require
        the connections to negotiate before sending data, or keep state on a connection. The result of this is that the DNS
        protocol scales much better than if it was sent over a stateful transport protocol like TCP. %TODO: More?
    \item[DNS part 2:] The use of TCP for DNS could have eliminated cache-poisoning attacks, because an attacker would then have
        to brute-force the 32-bit sequence number in the TCP packet in addition to the 16-bit DNS identification number.
        Such an attack would clealy be infeasible.

        The result of a cache-poisoning is that a DNS server caches an incorrect and malicious response, leading to malicious redirects
        of the requests. The attack may then be spread further by legitimate requests to the poisoned server, that are then cached in
        other servers. As an example one could attempt to poison the DNS server of a Danish ISP, redirecting all requests for common banks
        to a compromised server. This server could then infect users or steal their credentials. One might also be able to redirect
        the domains used to serve the NemID-applet, instead sending a compromised version to browsers.
    % TODO: May data be mixed with the FIN packets?
    \item[HTTP part 1:] The minimum number of packets is 3 for the handshake (where the last one can hold the request data because
        of the large MTU), 2 for the server ACK with corresponding data and the client ACK, and 4 for the closing of the connection.
        This results in a minimal number of 9 packets from a TCP perspective.
    % TODO: Correct if packages change
    \item[HTTP part 2:] Only 1/9 of the packets used for the connection actually transmit data. The justification for using
        TCP despite of this overhead is the fact that it provides the reliability needed by HTTP (as discussed in the next part), and
        that it allows for keeping connections open and thus reducing the setup overhead.
    \item[HTTP part 3:] The choice of UDP as a transport protocol for HTTP would be poor, because the guarantees provided by
        TCP are needed for HTTP transmissions. The use of HTTP does not allow for packets to be completely dropped (HTTP is not
        loss-tolerant), and the data stream must be presented in-order for the documents to make sense. In addition to this the
        HTTP protocol is naturally structured such that it fits the TCP model well, by defining a stream of requests and responses.
        %TODO: More?
\end{description}

\subsection{TCP: Principles and practice}
% Specify the point of view, is it from the client's or server's side (or both)?
\subsubsection{TCP headers}
\begin{description}
    \item[Part 1.1:] The purpose of the RST bit is to inform the sender of a segment that it's destination IP or port was
        incorrect, such that it will stop sending further segments or expect a connection to be set up. A TCP stack may return
        a RST packet if you attempt to send a SYN packet with a destination port that is not listening.
    \item[Part 1.2:] The sequence number header refers to the byte-stream number of the first byte in the sent segment. The
        acknowledgement number header refers to the segment number of the next expected byte to be received. The acknowledgement
        number header that is being sent in one direction is the sequence number of the last byte that was correctly received
        plus one. %TODO: Rewrite?
    \item[Part 1.3:] The purpose of the window is to enable flow control of TCP streams, such that a receiver is not overwhelmed
        by data. A positive window size indicates that the sender may continue to send data, as there is room in the receive buffer
        to store it.
    \item[Part 1.4:] If the window size of the receiver is 0 the sender is required to send segments of size 1, such
        that it may receive an ACK with an updated window size. If this was not the case then the sender might have been
        permanently blocked from sending, even though the window size of the receiver changed.
    \item[Part 2:] The sending of data in the third step (the ACK) of the 3-way-handshake is possible because the initial
        sequence numbers have already been correctly exchanged at that point. %TODO: More?
    \item[Part 3:] %TODO: Draw a diagram
\end{description}

\subsubsection{High performance TCP}
\begin{description}
    \item[Part 1:] The maximum possible number in receive window header is $2^{16}-1 = 65535$. This means that the throughput in one
        direction is limited to \[\frac{65525}{RTT} \text{ B/msec}\] %TODO: Rewrite?
    \item[Part 2:] Ignoring the overhead of TCP packet headers it would take a 100Mb/s connection
        \[ \frac{65535 * 8 \text{ bits}}{100 * 10^{6} \text{ bits/sec}} = 5.243 \text{ milliseconds} \]
        to send enough bytes to fill the receive window. We must therefore have $RTT \leq 5.243 \text{ milliseconds}$ to fully utilize
        the connection. %TODO: Calculate in another way?
    \item[Part 3:] 
\end{description}

\subsubsection{Flow and Congestion control}
\begin{description}
    \item[Part 1:] 
    \item[Part 2:] 
    \item[Part 3:] % At most 10 sentences
    \item[Part 4:] 
\end{description}
